The Three-HITs Theorem\footnote{This work was partially supported by COST Action CA15123.}

### 2017-03-20 Paper/Paper.tex
Fixed coherencies in elimination rule

Lastly, we define $H_\Approx$, and for this we make one more identification.
Instead of identifying points, we will identify paths in this step.
Since also paths are added during the construction, there might also be duplicated paths.
The resulting type should be free, so these paths should be identified.
We define a map $q : B_i \> R \rightarrow \sum (x, y : P), (x = y) \times (x = y)$ sending $x : B_i \> R$ to the pair
\[
(\overline{t_i} \> x, \overline{r_i} \> x, \ap \> (j_Q \circ \inn_1) \> (p_R \> x), p_Q \> (j_R \> x))
\]
Concluding the construction, we define $H_{\Approx}$ as $\pcoeq \> (B_i \> R) \> C_2 \> q$.

@@

Let us do this in the general case.
Suppose, we have a map $g : P \rightarrow \hocolim \> F \> f$, and that we already constructed $\varphi : \prod (x : P), Y(g \> x)$.
Our goal is to extended the map into a $\varphi' : \prod (x : H_{\rec} P), Y(c_{Y, \rec} \> x)$, and for that we use $H_{\rec}$-induction.
Note that for each $c'_{\rec} \> x$ with $x : A_{\rec} \> P$ we have the type $Y(c_{\rec} \> (A_{\rec} \> g \> x))$, and thus we have a type family on $H_{\rec}$.
Now let $x : A_{\rec} \> P$ and $y : \overline{A_{\rec}} \> Y \> x$ be given.
Then we need to give an element of the type $Y(c_{\rec} \> (A_{\rec} \> g \> x))$ for which we take $c_{Y,\rec} \> (A_{\rec} \> g \> x) \> y$.

Now we can also extend the map to $H_{\Con}^n \> P$, because we can define this map on each component.
On the component $P$ it is just $\varphi$, and on the other components we define it via extension.

Next we need to extend the map to $H_{\Approx}$.
This is done by the universal mapping property of the coequalizer, and that requires some steps.
First, to give an paths between the images of $t_i \> x$ and $r_i \> x$.
Note that the images of these are $\hatt_i \> x$ and $\hatr_i \> x$ respectively, and then $q_{Y, i}$ gives the desired paths..

Next we check the coherency conditions, and we start with the first.
We need to check that $\inn_1(\inC \> x)$ and $H_{\Con} \> \inC \> x$ get mapped to the same element for $x : H_{\Con}(F \> n)$.
To do so, we use a case distinction on $H_{\Con}(F \> n)$, and for the case $x \equiv \inn_1 \> y$ with $y : F \> n$, we have the following equations 
\begin{equation*}
\begin{split}
h \> (n+1) \> (\inn_1(\inC \> (\inn_1 \> y))) 
\equiv 
h \> (n+1) \> (\inn_1(f \> n \> y)),
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
h \> (n+1) \> (H_{\Con} \> (\inC \circ \inn_1) \> (\inn_1 \> y)) 
&\equiv 
h \> (n+1) \> (\inn_1(\inC(\inn_1 \> y)))
\\
&\equiv
h \> (n+1) \> (\inn_1(f \> n \> y)).
\end{split}
\end{equation*}
Here we use that $f \> x$ is defined to be $\inC(\inn_1 \> x)$.
Since they are definitionally equal, we can just use the path $\refl$.

For the other cases, we take a look at $c_{\rec}' \> y$.
\begin{equation*}
\begin{split}
h \> (n+1) \> (\inn_1(\inC \> (c_{\rec}' \> y))) 
&\equiv h \> (n+1) \> (\inC \> (c_{\rec}' \> y))\\
&\equiv h \> (n+1) \> (c_{\rec}' \> y)\\
&\equiv c_{Y, \rec} (h \> n \> y)
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
h \> (n+1) \> (H_{\Con} \> (\inC \circ \inn_1) \> (c_{\rec}' \> y)) 
&\equiv 
h \> (n+1) \> (c_{\rec}' \> (f \> n \> y))
\\
&\equiv
c_{Y, \rec} \> (h \> (n+1) \> (f \> n \> y)\\
&\equiv
c_{Y, \rec} \> (h \> (n+1) \> (\inC(\inn_1 \> y)).
\end{split}
\end{equation*}

By $\inl$ it gets mapped $\inl (c_{\rec}' \> x)$.
Since $h(n+1)$ is defined as the pushout map, it maps $\inl (c_{\rec}' \> x)$ to $h \> (n+1) \> (c_{\rec}' \> x) \equiv c_{Y, \rec}(h \> n \> x)$.
The map $H_{\Con} (f \> n)$ sends $c_{\rec}' \> x$ to $c_{\rec}' (f \> n \> x)$, and the dependent map $h$ sends it to $c_{Y, \rec}(h \> (n+1) \> (f \> x))$.
Using the definition of the pushout map, this is equal to $c_{Y, \rec}(h \> n \> x)$
Hence, this diagram commutes, and thus the first coherency is fine.
The equality between the points is $\refl$ as they are definitionally equal.

For the second coherency we need to check that

>>>>

Lastly, we define $H_\Approx$, and for this we make one more identification.
Instead of identifying points, we will identify paths in this step.
Since also paths are added during the construction, there might also be duplicated paths.
The resulting type should be free, so these paths should be identified.
We define a map $q : B_i \> R \rightarrow \sum (x, y : P), (x = y) \times (x = y)$ sending $x : B_i \> R$ to the pair
\[
(\overline{t_i} \> x, \overline{r_i} \> x, \ap \> (j_Q \circ \inn_1) \> (p_R \> x), p_Q \> (B_i \> j_R \> x))
\]
Concluding the construction, we define $H_{\Approx}$ as $\pcoeq \> (B_i \> R) \> C_2 \> q$.

@@

Let us do this in the general case.
Suppose, we have a map $g : P \rightarrow \hocolim \> F \> f$, and that we already constructed $\varphi : \prod (x : P), Y(g \> x)$.
Our goal is to extend the map into $\varphi' : \prod (x : H_{\rec} P), Y(c_{Y, \rec} \> x)$, and for that we use $H_{\rec}$-induction.
Note that for each $c'_{\rec} \> x$ with $x : A_{\rec} \> P$ we have the type $Y(c_{\rec} \> (A_{\rec} \> g \> x))$, and thus we have a type family on $H_{\rec}$.
Now let $x : A_{\rec} \> P$ and $y : \overline{A_{\rec}} \> Y \> x$ be given.
Then we need to give an element of the type $Y(c_{\rec} \> (A_{\rec} \> g \> x))$ for which we take $c_{Y,\rec} \> (A_{\rec} \> g \> x) \> y$.

Now we can also extend the map to $H_{\Con}^n \> P$, because we can define this map on each component.
On the component $P$ it is just $\varphi$, and on the other components we define it via extension.
We call this map $h_1$.

Next we need to extend the map to $H_{\Approx}$.
This is done by the universal mapping property of the coequalizer, and that requires some steps.
First, to give an paths between the images of $t_i \> x$ and $r_i \> x$.
Note that the images of these are $\hatt_i \> x$ and $\hatr_i \> x$ respectively, and then $q_{Y, i}$ gives the desired paths.
This gives an extension $h_2$ to $C_1$.

Next we check the coherency conditions, and we start with the first.
We need to check that $\inn_1(\inC \> x)$ and $H_{\Con} \> \inC \> x$ get mapped to the same element for $x : H_{\Con}(F \> n)$ by $h_2$.
To do so, we use a case distinction on $H_{\Con}(F \> n)$, and for the case $x \equiv \inn_1 \> y$ with $y : F \> n$, we have the following equations 
\begin{equation*}
\begin{split}
h_2 \> (\inC(\inn_1(\inC \> (\inn_1 \> y))))
&\equiv
h_1 \> (\inn_1(\inC \> (\inn_1 \> y))) \\
&\equiv 
h_1 \> (\inn_1(f \> n \> y))\\
&\equiv 
h_1 \> (\inn_1(\inC(\inn_1 \> y))),
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
h_2 \> (\inC(H_{\Con} \> (\inC \circ \inn_1) \> (\inn_1 \> y)))
&\equiv
h_1 \> (H_{\Con} \> (\inC \circ \inn_1) \> (\inn_1 \> y))\\
&\equiv 
h_1 \> (\inn_1(\inC(\inn_1 \> y)))
\end{split}
\end{equation*}
Here we use that $f \> n \> x$ is defined to be $\inC(\inn_1 \> x)$.
Since they are definitionally equal, we can just use the path $\refl$.

For the other cases, we take a look at $c_{\rec}' \> y$, and for $y$ we assume that $h_1(\inn_1(\inC \> y)) = h_1(H_{\Con} \> (\inC \circ \inn_1) \> y)$.
Note that at each level $h$ is defined using the eliminator of the coequalizer.
This means that $h \> n \> (\inC \> (c_{\rec}' \> y))$ and $c_{Y, \rec}(h \> n \> (\inC \> y))$ are equal by definition, and thus we can make the following computations.
\begin{equation*}
\begin{split}
h_1 \> (\inn_1(\inC \> (c_{\rec}' \> y))) 
&\equiv 
h \> n \> (\inC \> (c_{\rec}' \> y))\\
&
= c_{Y, \rec} (h \> n \> (\inC \> y))
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
h_1 \> (H_{\Con} \> (\inC \circ \inn_1) \> (c_{\rec}' \> y)) 
&\equiv 
h_1 \> (c_{\rec}' \> (H_{\Con} \> (\inC \circ \inn_1) \> y))
\\
&\equiv
c_{Y, \rec} \> (h_1 \> (H_{\Con} \> (\inC \circ \inn_1) \> y))\\
&=
c_{Y, \rec} \> (h_1(\inn_1(\inC \> y)))\\
&\equiv
c_{Y, \rec} \> (h \> n \> (\inC \> y)).
\end{split}
\end{equation*}

For the second coherency we need to check that the paths $\ap \> h_2 \> (\ap \> (f \> n) \> (p_i \> x))$ and $\ap \> h_2 \> (p_i \> (f \> n \> x))$ are equal.
Here we use several Lemmata, namely Lemma 2.2.2 from \cite{hottbook} and Lemma \ref{lem:pathext}.
For the first path we can show that it is equal to $q_{Y, i} \> (h \> n \> x)$.
\begin{equation*}
\begin{split}
\ap \> h_2 \> (\ap \> (f \> n) \> (p_i \> x))
&\equiv
\ap \> h_2 \> (\ap \> (\inC \circ \inn_1) \> (p_i \> x))\\
&=
\ap \> (h_2 \circ \inC) \> (\ap \> \inn_1 \> (p_i \> x))\\
&=
\ap \> h_1 \> (\ap \> \inn_1 \> (p_i \> x))\\
&=
\ap \> (h_1 \circ \inn_1) \> \> (p_i \> x)\\
&=
\ap \> (h \> n) \> \> (p_i \> x)\\
&\equiv
q_{Y, i} \> (h \> n \> x)
\end{split}
\end{equation*}
Since $(h_2 \circ \inC) \> x \equiv h_1 \> x$ and $(h_1 \circ \inn_1) \> x \equiv h \> n \> x$, we can use the path $\refl$, and thus the transport is the identity.
For the other path we can do the same.
\begin{equation*}
\begin{split}
\ap \> h_2 \> (p_i \> (f \> n \> x))
&\equiv
q_{Y, i} \> (h_2 \> (f \> n \> x))\\
&\equiv
q_{Y, i} \> (h_2 \> (\inC \> \inn_1 \> x))\\
&\equiv
q_{Y, i} \> (h_1 \> (\inn_1 \> x))\\
&\equiv
q_{Y, i} \> (h \> n \> x)
\end{split}
\end{equation*}
